Comparing order of acquisition cross-linguistically

### 2018-11-30 languages.Rmd
similarity based growth

cor_all <- cor_data %>%
  bind_rows(cor_random)

@@

ggplot(cor_all, 
      aes(x = tau, fill=data)) +
  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
                 binwidth=0.05)+
  #scale_x_log10() +
  theme_few() + 
  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
  scale_y_continuous(labels = scales::percent)+
  xlab("pairwise correlation") +ylab("Count")

@@

## Nouns

We begin with roughly the same data used by Hills. *(TODO fix, get same data)*

```{r warning=FALSE}
# We begin by importing data from wordbank. Age of aquisition (in months, it starts with 16, 17,..) is that at which 50% of children can produce the word. We also do naive triming at this point, this means we are ignoring homophone/polysemy (chiken (food), chiken (animals), etc,.. but we will have to be careful in our choices if we are preparing later for publication.

full_vocab <- make_vocab_dataframe(lang="English (American)",
                                   lang_form = "WS",
                                   lex_class = "nouns") %>%
  trim_all_unilemma() %>%
  trim_all_definition() %>%
  arrange(age) %>%            # keep first age for duplicates
  distinct(uni_lemma, .keep_all = TRUE) %>%
  select(uni_lemma, definition, age, category)
```

The initial vocabulary contains `r nrow(full_vocab)` (compared to Hills' 312).

## Perceptual & Conceptual Features

Features taken from McRae et al. (2005), in which features were collected for 541 nouns from 725 adults, with 30 adults providing  14 features for each noun.

```{r warning=FALSE, message=FALSE}
features <- load_features()
w2v <- load_w2v()

hills_vocab <- full_vocab %>%
  filter(age <= 30) %>%
  filter(uni_lemma %in% features$Concept) # filter to words with features

vocab <- hills_vocab %>%
  filter(uni_lemma %in% w2v$from | uni_lemma %in% w2v$to)
```

To begin our analysis, we only consider the words for which feature data are available, an overlap of `r nrow(hills_vocab)` in our data compared to Hills' 130. Then we filter the `r nrow(hills_vocab) - nrow(vocab)` words for which word2vec data is not available, for a final vocabulary of `r nrow(vocab)`.

## Build Network

Using vocabulary obtained by 30 months and the same McRae features as Hills, we construct a network with edge attributes for perceptual and conceptual features, and for word2vec similarity.

```{r message=FALSE}
# perceptual and conceptual McRae feature types
perceptual_features = c("sound", "taste", "smell", "tactile",
                        "visual-form_and_surface", "visual-motion", "visual-color")
conceptual_features = c("function")

# count shared features between words in vocabulary
perceptual_links <- make_feature_links(vocab = vocab,
                                       feature_types = perceptual_features) %>%
  rename(perceptual = shared)

conceptual_links <- make_feature_links(vocab = vocab,
                                       feature_types = conceptual_features) %>%
  rename(conceptual = shared)

# get word2vec distance between words in vocabulary
w2v_links <- make_w2v_links(vocab = vocab) #TODO still problem w/ vocab matching w2v data

links <- perceptual_links %>%
  full_join(conceptual_links, by=c("from", "to")) %>%
  full_join(w2v_links, by=c("from", "to"))

network <- graph_from_data_frame(links, vertices = vocab, directed = FALSE) %>%
  as_tbl_graph()
```

# Results

## The Network

First we generate a display layout for the network, based on the word2vec data.

```{r}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

layout <- layout_network(network %E>% mutate(weights = w2v_similarity))

network <- network %N>%
  mutate(x = layout[,1]) %>%
  mutate(y = layout[,2])
```

We can examine the networks generated by filtering edges with a word2vec similarity threshold.

```{r out.width = '100%', dpi=300}
source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

par(mfrow=c(2, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first

for (s in seq(0.35, 0.5, 0.05)) {
  plot_network(network %E>% filter(w2v_similarity > s),
               layout = layout,
               labels=TRUE,
               frame=FALSE,
               title=str_glue("Threshold = {s}"))
}

## Clustering algorithms

```{r out.width='100%', fig.asp=1/2, dpi=300}
# cluster_edge_betweenness - doesn't cluster reasonably, treats weights as distances?
# 
# cluster_infomap - returns one cluster
# 
# cluster_label_prop - returns one cluster
# 
# cluster_optimal - too computationally intensive for laptop, may not be possible (NP)

source(paste(getwd(),"/helpers/all_helper.r",sep = ""), chdir = T)

par(mfrow=c(1, 2), mar=c(2,0.4,0.8,0.4)) # row x col, column first

feature_network <- network %E>%
  mutate_all(funs(replace(., is.na(.), 0))) %>%
  mutate(features = perceptual + conceptual) %>%
  filter(features > 0)

# cluster_fast_greedy
plot_network(network, layout = layout,
             clusters = cluster_fast_greedy(network,
                                            weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_fast_greedy(feature_network,
                                            weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_leading_eigen
plot_network(network, layout = layout,
             clusters = cluster_leading_eigen(network,
                                              weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_leading_eigen(feature_network,
                                              weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_louvain
plot_network(network, layout = layout,
             clusters = cluster_louvain(network,
                                        weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_louvain(feature_network,
                                        weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_spinglass
plot_network(network, layout = layout,
             clusters = cluster_spinglass(network,
                                          weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_spinglass(feature_network,
                                          weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)

# cluster_walktrap
plot_network(network, layout = layout,
             clusters = cluster_walktrap(network,
                                         weights = E(network)$w2v_similarity)$membership,
             labels=TRUE, frame=TRUE)

plot_network(feature_network, layout = layout,
             clusters = cluster_walktrap(feature_network,
                                         weights = E(feature_network)$features)$membership,
             labels=TRUE, frame=TRUE)
```

```{r out.width='100%', fig.asp=1/2, dpi=300}
# cluster_walktrap
for (age_limit in seq(16, 30, by=2)) {
  net_at_age <- network %N>% filter(age <= age_limit) %E>% mutate(weights = w2v_similarity)

  plot_network(net_at_age,
               clusters = cluster_walktrap(net_at_age,
                                           weights = E(net_at_age)$w2v_similarity)$membership,
               labels = TRUE,
               frame = TRUE)
}
```

```{r}
feature_net <- network %E>% mutate(weights = perceptual) %E>% filter(weights > 0) %N>% filter(!node_is_isolated())
feature_layout <- layout_network(feature_net)

feature_net <- feature_net %N>%
  mutate(x = feature_layout[,1]) %>%
  mutate(y = feature_layout[,2])

```{r out.width='100%', fig.asp=1/2, dpi=300}
# cluster_walktrap
for (age_limit in seq(16, 30, by=2)) {
  net_at_age <- feature_net %N>% filter(age <= age_limit) %E>% mutate(weights = perceptual)

  plot_network(net_at_age,
               clusters = cluster_walktrap(net_at_age,
                                           weights = E(net_at_age)$perceptual)$membership,
               labels = TRUE,
               frame = TRUE)
}
```

>>>>

similarity-based learning mechanism
```{r}

unilemmas <- (data_by_lang[[3]] %>% #English (I should recode this to be more explcit)
    filter(!is.na(uni_lemma)) %>%
    trim_all_unilemma() %>%
    select(uni_lemma) %>%
    #(uni_lemma))$uni_lemma
    unique())$uni_lemma

#get the data frame for w2v
w2v <- load_w2v() %>%
  filter(from %in% unilemmas & to  %in% unilemmas)

#Transfom the data fram into adjencency matrix
g <- graph.data.frame(w2v, directed=FALSE)
  #matrix_sim <- get.adjacency(g, attr="w2v_similarity", sparse=FALSE)
  matrix_sim <- get.adjacency(g, attr="w2v_similarity")

vocab <- names(matrix_sim[word_0, ])
#Now generate a sequence based on the first word

sim_learning <- function() {
  seq_gen <- function(word_t0, sequence_t0) {

    if (length(sequence_t0) == length(matrix_sim[word_t0, ])) {
      return (sequence_t0)
    } else {
      #generate similarity values of all words to word_t
      all_words <- matrix_sim[word_t0, ]
      #Obtain indices of the words already known at time t (present in in sequence_t)
      indices <- which(names(all_words) %in% sequence_t0)
      #generate candidates for word_t+1 by subseting known words from all words
      candidates <- all_words[-indices]
      #the next word (i.e., word_t+1) is the most simialr to the last word acquired ()
      index_t1 <- which.max(candidates)
      word_t1 <- names(index_t1)
      sequence_t1 <- c(sequence_t0, word_t1)

      return(seq_gen(word_t1, sequence_t1))
    }
  }

  word_0 <- sample(vocab, 1) # this is the only random compoenent
  sequence_0 <- c(word_0)
  #seq_gen(word_0, sequence_0)
  return(seq_gen(word_0, sequence_0))
}

pair_sim <- function(lang1){
  pair_cor_sim <- function (lang2){

  #Orering based on word similarity

  #Real ordering in the language 
  data_lang1 <- lang1 %>%
    filter(!is.na(uni_lemma)) %>%
    trim_all_unilemma() %>%
    filter(uni_lemma %in% vocab) %>% #Intersection with w2v data
    select(uni_lemma, aoa) %>%
    group_by(uni_lemma) %>%
    summarise(aoa1=mean(aoa))

  #Orering based on word similarity
  sim_list <- sim_learning()
  sim_data <- data.frame(uni_lemma=sim_list, orderSim = seq(1, length(sim_list)))

  #Combine both
  both_orders <- data_lang1 %>%
    left_join(sim_data) %>%
    filter(!is.na(orderSim),
           !is.na(aoa1))

  order_lang1 <- rank(both_orders$aoa1)
  order_sim <- rank(both_orders$orderSim)

  mycorr <- cor.test(order_lang1, order_sim, method = 'kendall')

}
  map(data_by_lang, pair_cor_sim) %>%
    bind_rows()

cor_sim <- map(data_by_lang, pair_sim) %>%
  bind_rows() %>%
  mutate(data="sim")

cor_all <- cor_data %>%
  bind_rows(cor_random) %>%
  bind_rows(cor_sim)

@@

ggplot(cor_all, 
      aes(x = tau, fill=data)) +
  geom_histogram(aes(y = (..count..)/tapply(..count..,..PANEL..,sum)[..PANEL..]),
                 alpha=0.5,
                 binwidth=0.05)+
  #scale_x_log10() +
  theme_few() + 
  theme(aspect.ratio = 0.7, legend.title = element_text(size=8)) +  #facet_grid(Segmentation ~ language)+
  scale_y_continuous(labels = scales::percent)+
  xlab("pairwise correlation") +ylab("Count")

@@
